### 2013-03-01 doc/final_report/testing.tex
Added more documentation for testing

@@

@@

After a suitably large number of papers were collected and annotated, the
papers were partitioned into disjoint \emph{training} set and a \emph{testing}
sets.

>>>>

Nose for python is an extension of Python's built in Unit testing module that
is supposed to make setting up a testing environment and reusing test code
easier. Unit tests for Patridge's webserver backend and paper preprocessor were
written and maintained throughout the project. As each new feature was added to
the system, the whole suite of tests was executed to provide integration
coverage and make sure that new features did not break existing code.

@@

The frontend parts of Partridge that were written in Javascript and HTML5 also
had to be tested to verify that the query and upload forms behaved as expected.

@@

After a suitably large number of papers were collected and annotated, the
papers were partitioned into disjoint \emph{training} and \emph{testing}
sets. The decision tree that is used to classify a paper's "type"
